Data Exploration: IUCN and AquaMaps

### 2016-09-24 clip_fao/fao_clip_pac.Rmd
unbolded legend for map

### Select four example species
spp_ex <- c('Hoplichthys regani' = 'Fis-34036', 
            'Ipnops meadi'       = 'Fis-143854', 
            'Culeolus herdmani'  = 'URM-2-3539', 
            'Chrionema chlorotaenia' = 'Fis-33989')

@@

  rast_map <- rast_spp_map +
    tm_shape(spp_occur_pts) + 
      tm_bubbles(col = 'obs',
                 title.col = 'Occurrences ',
                 palette = c('red', 'blue', 'green'),
                 border.col = 'red',
                 border.lwd = 0.25,
                 border.alpha = 1,
                 size = 1,
                 scale = .3,
                 alpha = .3) +
      # tm_dots(col = 'red') +
    tm_layout(# title = spp_name,
              title.position = c('left', 'bottom'),
              fontface = 'bold.italic',
              fontfamily = 'Helvetica',
              title.size = .8,
              frame = TRUE,
              legend.text.size = .6,
              legend.title.size = .7,
              legend.outside = FALSE,
              legend.position = c('right', 'top'),
              legend.bg.color = 'white',
              legend.bg.alpha = .95,
              attr.outside = TRUE)

>>>>

### Select four example species
spp_ex <- c('Hoplichthys regani' = 'Fis-34036', 
            'Ipnops meadi'       = 'Fis-143854', 
            'Culeolus herdmani'  = 'URM-2-3539', 
            'Chrionema chlorotaenia' = 'Fis-33989')[1]

@@

  rast_map <- rast_spp_map +
    tm_shape(spp_occur_pts) + 
      tm_bubbles(col = 'obs',
                 title.col = 'Occurrences ',
                 palette = c('red', 'blue', 'green'),
                 border.col = 'red',
                 border.lwd = 0.5,
                 border.alpha = 1,
                 size = 1,
                 scale = .4,
                 alpha = .3) +
      # tm_dots(col = 'red') +
    tm_layout(frame = TRUE,
              legend.text.size = .6,
              legend.title.size = .7,
              legend.outside = FALSE,
              legend.position = c('right', 'top'),
              legend.bg.color = 'white',
              legend.bg.alpha = .95,
              attr.outside = TRUE)
